### 2021-11-06 NSF2021/Description/specificaim3.tex

>>>>

Within this framework, we will first investigate the interaction between two Janus particles under HAP in an electrolytic solution described by the above
equations. We will conduct analytical calculations to investigate the effects of ion transport on the hydrophobic attraction between two Janus particles using the reciprocal theorem as in \cite{BayatiNajafi2016} for two Janus particles with a small surface activity.
